pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-03-18 article.tex
Minor processsing of feedback

The first step in \verb;pirouette; is to simulate a DNA alignment from the 
given phylogeny. 
To do so, we must specify an alignment model $\mathit{A}$ which consists of: a 
DNA root sequence $\mathit{r_{s}}$, the DNA mutation rate $\mathit{m_{r}}$, a
site model $\mathit{s_{m}}$ (in this context: a nucleotide substitution model) 
and a clock model $\mathit{c_{m}}$. 
In this example, the DNA root sequence consists in four blocks of 250 
nucleotides each, 
where the per-nucleotide mutation rate is 0.1 mutations per unit time.
We use a Jukes-Cantor (JC, \cite{jukes1969evolution}) site model
and a strict clock model as these are the simplest.
A Jukes-Cantor site model,
assumes that mutation rates between nucleotides are equal and constant. 
A strict clock model assumes that the mutation rates 
of all species are equal and constant.

@@

\giovanni{I think we are providing too many information}
\richel{agreed, thanks for pushing back}

The error distribution returned by \verb;pir_run; is stored as a data frame. It 
can be directly plotted using \verb;pir_plot;:

@@

The error distribution obtained is shown as a violin plot
in figure~\ref{fig:example_1}.

>>>>

The first step in \verb;pirouette; is to simulate a DNA alignment from the 
given phylogeny. 
To do so, we must specify an alignment model $\mathit{A}$ which consists of: a 
DNA root sequence $\mathit{r_{s}}$, the DNA mutation rate $\mathit{m_{r}}$, a
site model $\mathit{s_{m}}$ (in this context: a nucleotide substitution model) 
and a clock model $\mathit{c_{m}}$. 
In this example, the DNA root sequence consists in four blocks of 250 
nucleotides each, 
where the per-nucleotide mutation rate is 0.1 mutations per unit time.
We use a Jukes-Cantor (JC, \cite{jukes1969evolution}) site model
and a strict clock model as these are the simplest.
A Jukes-Cantor site model
assumes that mutation rates between nucleotides are equal and constant. 
A strict clock model assumes that the mutation rates 
of all species are equal and constant.

@@

The error distribution returned by \verb;pir_run; is stored as a data frame. 
\richel{
  I suggest \texttt{pir\_run} to return a list of run experiments,
  as described in Issue 225, 
  \url{https://github.com/richelbilderbeek/pirouette/issues/225}
}
It can be directly plotted using \verb;pir_plot;:

@@

The error distribution obtained is shown as a violin plot
in figure~\ref{fig:example_1}
\richel{
  I suggest to use a histogram (or density plot) instead:
  I like how the error distribution in figure 1 looks.
}
.
